---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# IPO2

<!-- badges: start -->
<!-- badges: end -->

Isotopologue Parameter Optimization (IPO) is a commonly used tool to optimize parameters for XCMS analysis of metabolomics data. The progress in XCMS development has made it more difficult to utilize IPO, and so IPO2 is an effort to more seamlessly integrate this method of parameter optimization with the latest version of XCMS. While this package adopts a similar approach of using isotope identification, scoring, and design-of-experiments, the underlying code to accomplish these tasks is different and the results are likely not exactly the same. 

Please find a copy of the original IPO manuscript in the source of this package. 

```{r}
citation("IPO")
```


## Installation

You can install the original release version of IPO from [Bioconductor](https://www.bioconductor.org/packages/release/bioc/html/IPO.html). 

``` r
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("IPO")
```

And the development version is available from [GitHub](https://github.com/rietho/IPO). 

``` r
if (!requireNamespace("devtools", quietly = TRUE))
    install.packages("devtools")
    
devtools::install_github("rietho/IPO")
```

You can install the development version of IPO2 from [GitHub](https://github.com/rietho/IPO2) with:

``` r
if (!requireNamespace("devtools", quietly = TRUE))
    install.packages("devtools")
    
devtools::install_github("wmoldham/IPO2")
```
